Human judgement forecasting of COVID-19 in the UK

### 2023-05-04 manuscript/manuscript.tex
update data availablity information and citation for SI

\subsection*{Data availability}
All data and ode are available publicy under a MIT license under \url{https://github.com/epiforecasts/uk-crowd-forecasting-challenge}.

>>>>

\subsection*{Data availability}
All data and code are available publicy under a MIT license under \url{https://github.com/epiforecasts/uk-crowd-forecasting-challenge} and \url{https://doi.org/10.5281/zenodo.7897257}. The data has been published separately here: \url{https://doi.org/10.5281/zenodo.7897289}. 
Supplementary information \cite{bosseSupplementaryInformationHuman2023} to this manuscript is available at \url{https://doi.org/10.5281/zenodo.7897513}.
